Model LF

### 2022-12-20 paper version 2.Rmd
Commit

COMMENT> 
BEHAVIORAL> emp_old
EQ> emp_old = p_250 * (yk/prodk) 
COEFF> p_250 
STORE> coe(14)

COMMENT> 
BEHAVIORAL> emp_sens
EQ> emp_sens = p_251 * (yk/prodk) 
COEFF> p_251 
RESTRICT> p_251 = 0.5
STORE> coe(144)

COMMENT> 
IDENTITY> emp
EQ> emp = emp_old
IF> sens_3 <= 0
IDENTITY> emp
EQ> emp = emp_sens
IF> sens_3 > 0

@@

```{r}
###Gengivelse af stød til model
part_bs1 = Shock_bs1$simulation$part
unemp_bs1 = Shock_bs1$simulation$unemp
komp_r_bs1 = Shock_bs1$simulation$komp_r
part_bs1 = Shock_bs1$simulation$part
yk_ds_bs1 = Shock_bs1$simulation$yk_ds
pc_ds_bs1 = Shock_bs1$simulation$pc_ds
wage_ds_t_bs1 = Shock_bs1$simulation$wage_ds_t
ur_ds_bs1 = Shock_bs1$simulation$ur_ds
emp_bs1 = Shock_bs1$simulation$emp
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
pconk_ds_bs1= Shock_bs1$simulation$pconk_ds
tilpas_pr_bs1 = Shock_bs1$simulation$tilpas_pr
u_ds_bs1 = Shock_bs1$simulation$u_ds
part_bs1 = Shock_bs1$simulation$part
nben_h_bs1 = Shock_bs1$simulation$nben_h
wage_ds_bs1 = Shock_bs1$simulation$wage_ds
dp_person_bs1 = Shock_bs1$simulation$dp_person
kont_h_ratio_bs1 = Shock_bs1$simulation$kont_h_ratio
unemp_bs1 = Shock_bs1$simulation$unemp
nl_g_bs1 = Shock_bs1$simulation$nl_g
inflation_bs1 = Shock_bs1$simulation$inflation
lf_bs1 = Shock_bs1$simulation$lf
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
wage_gap1_bs1 = Shock_bs1$simulation$wage_gap1
wage_gap_bs1 = Shock_bs1$simulation$wage_gap
prod_bs1 = Shock_bs1$simulation$prod
prodk_ds_bs1 = Shock_bs1$simulation$prodk_ds
max_dp_bs1 = Shock_bs1$simulation$max_dp
wage_ds_t_bs1 = Shock_bs1$simulation$wage_ds_t
xk_ds_bs1 = Shock_bs1$simulation$xk_ds
mk_ds_bs1 = Shock_bs1$simulation$mk_ds
lf_bs1 = Shock_bs1$simulation$lf
net_balance_bs1 = xk_ds_bs1 - mk_ds_bs1
net_balance_bs1_ratio= (xk_ds_bs1 - mk_ds_bs1)/yk_ds_bs1
nben_h_un_bs1 = Shock_bs1$simulation$nben_h_un

@@

```{r}
###Gengivelse af stød til model
max_dp_bs2 = Shock_bs2$simulation$max_dp
wage_bs2 = Shock_bs2$simulation$wage
komp_r_bs2 = Shock_bs2$simulation$komp_r
part_bs2 = Shock_bs2$simulation$part
yk_ds_bs2 = Shock_bs2$simulation$yk_ds
pc_ds_bs2 = Shock_bs2$simulation$pc_ds
wage_ds_t_bs2 = Shock_bs2$simulation$wage_ds_t
ur_ds_bs2 = Shock_bs2$simulation$ur_ds
emp_bs2 = Shock_bs2$simulation$emp
yd_hk_ds_bs2 = Shock_bs2$simulation$yd_hk_ds
pconk_ds_bs2= Shock_bs2$simulation$pconk_ds
tilpas_pr_bs2 = Shock_bs2$simulation$tilpas_pr
u_ds_bs2 = Shock_bs2$simulation$u_ds
part_bs2 = Shock_bs2$simulation$part
nben_h_bs2 = Shock_bs2$simulation$nben_h
wage_ds_bs2 = Shock_bs2$simulation$wage_ds
dp_person_bs2 = Shock_bs2$simulation$dp_person
kont_h_ratio_bs2 = Shock_bs2$simulation$kont_h_ratio
unemp_bs2 = Shock_bs2$simulation$unemp
nl_g_bs2 = Shock_bs2$simulation$nl_g
inflation_bs2 = Shock_bs2$simulation$inflation
lf_bs2 = Shock_bs2$simulation$lf
yd_hk_ds_bs2 = Shock_bs2$simulation$yd_hk_ds
wage_gap1_bs2 = Shock_bs2$simulation$wage_gap1
wage_gap_bs2 = Shock_bs2$simulation$wage_gap
prod_bs2 = Shock_bs2$simulation$prod
prod_bs2 = Shock_bs2$simulation$prod
ws_bs2 = Shock_bs2$simulation$ws
xk_ds_bs2 = Shock_bs2$simulation$xk_ds
mk_ds_bs2 = Shock_bs2$simulation$mk_ds
nben_h_un_bs2 = Shock_bs2$simulation$nben_h_un

net_balance_bs2 = xk_ds_bs2 - mk_ds_bs2
net_balance_bs2_ratio= (xk_ds_bs2 - mk_ds_bs2)/yk_ds_bs2

@@

```{r}
###Gengivelse af stød til model
max_dp_bs3 = Shock_bs3$simulation$max_dp
wage_bs3 = Shock_bs3$simulation$wage
komp_r_bs3 = Shock_bs3$simulation$komp_r
part_bs3 = Shock_bs3$simulation$part
yk_ds_bs3 = Shock_bs3$simulation$yk_ds
pc_ds_bs3 = Shock_bs3$simulation$pc_ds
wage_ds_t_bs3 = Shock_bs3$simulation$wage_ds_t
ur_ds_bs3 = Shock_bs3$simulation$ur_ds
emp_bs3 = Shock_bs3$simulation$emp
yd_hk_ds_bs3 = Shock_bs3$simulation$yd_hk_ds
nben_h_un_bs3 = Shock_bs3$simulation$nben_h_un

tilpas_pr_bs3 = Shock_bs3$simulation$tilpas_pr
u_ds_bs3 = Shock_bs3$simulation$u_ds
part_bs3 = Shock_bs3$simulation$part
nben_h_bs3 = Shock_bs3$simulation$nben_h
wage_ds_bs3 = Shock_bs3$simulation$wage_ds
dp_person_bs3 = Shock_bs3$simulation$dp_person
kont_h_ratio_bs3 = Shock_bs3$simulation$kont_h_ratio

nl_g_bs3 = Shock_bs3$simulation$nl_g
unemp_bs3 = Shock_bs3$simulation$unemp
s_h_bs3 = Shock_bs3$simulation$s_h
inflation_bs3 = Shock_bs3$simulation$inflation

yd_hk_ds_bs3 = Shock_bs3$simulation$yd_hk_ds
wage_gap1_bs3 = Shock_bs3$simulation$wage_gap1
wage_gap_bs3 = Shock_bs3$simulation$wage_gap
prod_bs3 = Shock_bs3$simulation$prod
prod_ds_bs3 = Shock_bs3$simulation$prod_ds
prod_ds_shock_bs3 = Shock_bs3$simulation$prod_ds_shock

@@

shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q')
)

@@

```{r}
###Gengivelse af stød til model
max_dp_bs4 = Shock_bs4$simulation$max_dp
wage_bs4 = Shock_bs4$simulation$wage
komp_r_bs4 = Shock_bs4$simulation$komp_r
part_bs4 = Shock_bs4$simulation$part
yk_ds_bs4 = Shock_bs4$simulation$yk_ds
pc_ds_bs4 = Shock_bs4$simulation$pc_ds
wage_ds_t_bs4 = Shock_bs4$simulation$wage_ds_t
ur_ds_bs4 = Shock_bs4$simulation$ur_ds
emp_bs4 = Shock_bs4$simulation$emp
yd_hk_ds_bs4 = Shock_bs4$simulation$yd_hk_ds
lf_bs4 = Shock_bs4$simulation$lf
tilpas_pr_bs4 = Shock_bs4$simulation$tilpas_pr
u_ds_bs4 = Shock_bs4$simulation$u_ds
part_bs4 = Shock_bs4$simulation$part
nben_h_bs4 = Shock_bs4$simulation$nben_h
wage_ds_bs4 = Shock_bs4$simulation$wage_ds
dp_person_bs4 = Shock_bs4$simulation$dp_person
kont_h_ratio_bs4 = Shock_bs4$simulation$kont_h_ratio

nl_g_bs4 = Shock_bs4$simulation$nl_g
unemp_bs4 = Shock_bs4$simulation$unemp
s_h_bs4 = Shock_bs4$simulation$s_h
inflation_bs4 = Shock_bs4$simulation$inflation

yd_hk_ds_bs4 = Shock_bs4$simulation$yd_hk_ds
wage_gap1_bs4 = Shock_bs4$simulation$wage_gap1
wage_gap_bs4 = Shock_bs4$simulation$wage_gap
prod_bs4 = Shock_bs4$simulation$prod
prod_ds_bs4 = Shock_bs4$simulation$prod_ds
prod_ds_shock_bs4 = Shock_bs4$simulation$prod_ds_shock

@@

```{r}
###Gengivelse af stød til model
max_dp_01 = Shock_1$simulation$max_dp
wage_01 = Shock_1$simulation$wage
komp_r_01 = Shock_1$simulation$komp_r
part_01 = Shock_1$simulation$part
yk_ds_01 = Shock_1$simulation$yk_ds
pc_ds_01 = Shock_1$simulation$pc_ds
wage_ds_t_01 = Shock_1$simulation$wage_ds_t
ur_ds_01 = Shock_1$simulation$ur_ds
emp_01 = Shock_1$simulation$emp
yd_hk_ds_01 = Shock_1$simulation$yd_hk_ds
nben_h_un_01 = Shock_1$simulation$nben_h_un

tilpas_pr_01 = Shock_1$simulation$tilpas_pr
u_ds_01 = Shock_1$simulation$u_ds
part_01 = Shock_1$simulation$part
nben_h_01 = Shock_1$simulation$nben_h
wage_ds_01 = Shock_1$simulation$wage_ds
dp_person_01 = Shock_1$simulation$dp_person
kont_h_ratio_01 = Shock_1$simulation$kont_h_ratio

nl_g_01 = Shock_1$simulation$nl_g
unemp_01 = Shock_1$simulation$unemp
yd_hk_ds_01 = Shock_1$simulation$yd_hk_ds
wage_gap1_01 = Shock_1$simulation$wage_gap1
wage_gap_01 = Shock_1$simulation$wage_gap
prod_01 = Shock_1$simulation$prod
```

```{r}
plot(part_01, col= "red"); lines(part_bs4, col = "blue");
legend("top",legend=c("Baseline", "Data"),lty=c(1,1),lwd=c(2),bty="n", col = c("red", "blue")); 
grid()
```

```{r}
plot(lf_01, col= "red"); lines(lf_bs4, col = "blue");
legend("top",legend=c("Baseline", "Data"),lty=c(1,1),lwd=c(2),bty="n", col = c("red", "blue")); 
grid()

@@

```{r}
plot((unemp_04-unemp_bs4)*1000, col= "red");

plot((lf_04-lf_bs4)*1000, col= "red");

plot((emp_04-emp_bs4)*1000, col= "red");
```

@@

nben_h_un_02 = Shock_2$simulation$nben_h_un
yk_ds_02 = Shock_2$simulation$yk_ds
emp_02 = Shock_2$simulation$emp
wage_ds_02 = Shock_2$simulation$wage_ds
ur_ds_02 = Shock_2$simulation$ur_ds
pc_ds_02 = Shock_2$simulation$pc_ds
yd_hk_ds_02 = Shock_2$simulation$yd_hk_ds
pconk_ds_02 = Shock_2$simulation$pconk_ds
komp_r_02 = Shock_2$simulation$komp_r
max_dp_02 = Shock_2$simulation$max_dp
nben_h_02 = Shock_2$simulation$nben_h
yd_hk_ds_02 = Shock_2$simulation$yd_hk_ds
ik_02 = Shock_2$simulation$ik
wage_ds_t_02 = Shock_2$simulation$wage_ds_t
nben_h_un_02 = Shock_2$simulation$nben_h_un
nl_g_02 = Shock_2$simulation$nl_g
nsben_h_02 = Shock_2$simulation$nsben_h
dp_person_02 = Shock_2$simulation$dp_person
xk_ds_02 = Shock_2$simulation$xk_ds
mk_ds_02 = Shock_2$simulation$mk_ds
ik_02 = Shock_2$simulation$ik
rer_02 = Shock_2$simulation$rer
ps_ds_02 = Shock_2$simulation$ps_ds
i_bd_nfc_k_ds_02 = Shock_2$simulation$i_bd_nfc_k_ds
yd1_hk_ds_02 = Shock_2$simulation$yd1_hk_ds
yd2a_hk_ds_02 = Shock_2$simulation$yd2a_hk_ds
yd2b_hk_02 = Shock_2$simulation$yd2b_hk
i_equip_nfc_k_ds_02 = Shock_2$simulation$i_equip_nfc_k_ds
u_ds_02 = Shock_2$simulation$u_ds
wage_gap1_02 = Shock_2$simulation$wage_gap1
gk_02 = Shock_2$simulation$gk
kont_h_ratio_02 = Shock_2$simulation$kont_h_ratio
lf_02 = Shock_2$simulation$lf
wage_gap_02 = Shock_2$simulation$wage_gap
max_gap_02 = Shock_2$simulation$max_gap
unemp_02 = Shock_2$simulation$unemp
inflation_02 = Shock_2$simulation$inflation
prod_02 = Shock_2$simulation$prod
ws_02 = Shock_2$simulation$ws
net_balance_02 = xk_ds_02 - mk_ds_02
```

@@

yk_ds_03 = Shock_3$simulation$yk_ds
emp_03 = Shock_3$simulation$emp
wage_ds_03 = Shock_3$simulation$wage_ds
ur_ds_03 = Shock_3$simulation$ur_ds
pc_ds_03 = Shock_3$simulation$pc_ds
yd_hk_ds_03 = Shock_3$simulation$yd_hk_ds
pconk_ds_03 = Shock_3$simulation$pconk_ds
komp_r_03 = Shock_3$simulation$komp_r
max_dp_03 = Shock_3$simulation$max_dp
nben_h_03 = Shock_3$simulation$nben_h
yd_hk_ds_03 = Shock_3$simulation$yd_hk_ds
ik_03 = Shock_3$simulation$ik
wage_ds_t_03 = Shock_3$simulation$wage_ds_t
nben_h_un_03 = Shock_3$simulation$nben_h_un
nl_g_03 = Shock_3$simulation$nl_g
nsben_h_03 = Shock_3$simulation$nsben_h
dp_person_03 = Shock_3$simulation$dp_person
part1_03 = Shock_3$simulation$part1
u_ds_03 = Shock_3$simulation$u_ds
kont_h_ratio_03 = Shock_3$simulation$kont_h_ratio
part_03 = Shock_3$simulation$part
unemp_03 = Shock_3$simulation$unemp
rw_ds_03 = Shock_3$simulation$rw_ds
kuld_03 = Shock_3$simulation$shock_kuld
inflation_03 = Shock_3$simulation$inflation
lf_03 = Shock_3$simulation$lf
prod_03 = Shock_3$simulation$prod
nben_h_un_03 = Shock_3$simulation$nben_h_un

@@

```{r}
# Define add-factor list (defining shock)
constantAdjList_4 <- list(
 shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q')
)

@@

```{r}
plot((unemp_04-unemp_bs4)*1000, col= "red");

plot((lf_04-lf_bs4)*1000, col= "red");

plot((emp_04-emp_bs4)*1000, col= "red");
```

>>>>

COMMENT> 
BEHAVIORAL> emp
EQ> emp = p_250 * (yk/prodk) 
COEFF> p_250 
STORE> coe(14)

@@

```{r}
###Gengivelse af stød til model
yk_ds_bs1 = Shock_bs1$simulation$yk_ds
unemp_bs1 = Shock_bs1$simulation$unemp
komp_r_bs1 = Shock_bs1$simulation$komp_r
part_bs1 = Shock_bs1$simulation$part
yk_bs1 = Shock_bs1$simulation$yk
y_bs1 = Shock_bs1$simulation$y
pc_ds_bs1 = Shock_bs1$simulation$pc_ds
wage_ds_t_bs1 = Shock_bs1$simulation$wage_ds_t
ur_ds_bs1 = Shock_bs1$simulation$ur_ds
emp_bs1 = Shock_bs1$simulation$emp
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
pconk_ds_bs1= Shock_bs1$simulation$pconk_ds
tilpas_pr_bs1 = Shock_bs1$simulation$tilpas_pr
u_ds_bs1 = Shock_bs1$simulation$u_ds
part_bs1 = Shock_bs1$simulation$part
nben_h_bs1 = Shock_bs1$simulation$nben_h
wage_ds_bs1 = Shock_bs1$simulation$wage_ds
dp_person_bs1 = Shock_bs1$simulation$dp_person
kont_h_ratio_bs1 = Shock_bs1$simulation$kont_h_ratio
unemp_bs1 = Shock_bs1$simulation$unemp
nl_g_bs1 = Shock_bs1$simulation$nl_g
inflation_bs1 = Shock_bs1$simulation$inflation
lf_bs1 = Shock_bs1$simulation$lf
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
wage_gap1_bs1 = Shock_bs1$simulation$wage_gap1
wage_gap_bs1 = Shock_bs1$simulation$wage_gap
prod_bs1 = Shock_bs1$simulation$prod
prodk_ds_bs1 = Shock_bs1$simulation$prodk_ds
max_dp_bs1 = Shock_bs1$simulation$max_dp
wage_ds_t_bs1 = Shock_bs1$simulation$wage_ds_t
xk_ds_bs1 = Shock_bs1$simulation$xk_ds
mk_ds_bs1 = Shock_bs1$simulation$mk_ds
lf_bs1 = Shock_bs1$simulation$lf
net_balance_bs1 = xk_ds_bs1 - mk_ds_bs1
net_balance_bs1_ratio= (xk_ds_bs1 - mk_ds_bs1)/yk_ds_bs1
nben_h_un_bs1 = Shock_bs1$simulation$nben_h_un
ur_bs1 = Shock_bs1$simulation$ur

@@

```{r}
###Gengivelse af stød til model
max_dp_bs2 = Shock_bs2$simulation$max_dp
wage_bs2 = Shock_bs2$simulation$wage
komp_r_bs2 = Shock_bs2$simulation$komp_r
part_bs2 = Shock_bs2$simulation$part
yk_bs2 = Shock_bs2$simulation$yk
yk_ds_bs2 = Shock_bs2$simulation$yk_ds
pc_ds_bs2 = Shock_bs2$simulation$pc_ds
wage_ds_t_bs2 = Shock_bs2$simulation$wage_ds_t
ur_ds_bs2 = Shock_bs2$simulation$ur_ds
emp_bs2 = Shock_bs2$simulation$emp
yd_hk_ds_bs2 = Shock_bs2$simulation$yd_hk_ds
pconk_ds_bs2= Shock_bs2$simulation$pconk_ds
tilpas_pr_bs2 = Shock_bs2$simulation$tilpas_pr
u_ds_bs2 = Shock_bs2$simulation$u_ds
part_bs2 = Shock_bs2$simulation$part
nben_h_bs2 = Shock_bs2$simulation$nben_h
wage_ds_bs2 = Shock_bs2$simulation$wage_ds
dp_person_bs2 = Shock_bs2$simulation$dp_person
kont_h_ratio_bs2 = Shock_bs2$simulation$kont_h_ratio
unemp_bs2 = Shock_bs2$simulation$unemp
nl_g_bs2 = Shock_bs2$simulation$nl_g
inflation_bs2 = Shock_bs2$simulation$inflation
lf_bs2 = Shock_bs2$simulation$lf
yd_hk_ds_bs2 = Shock_bs2$simulation$yd_hk_ds
wage_gap1_bs2 = Shock_bs2$simulation$wage_gap1
wage_gap_bs2 = Shock_bs2$simulation$wage_gap
prod_bs2 = Shock_bs2$simulation$prod
prod_bs2 = Shock_bs2$simulation$prod
ws_bs2 = Shock_bs2$simulation$ws
xk_ds_bs2 = Shock_bs2$simulation$xk_ds
mk_ds_bs2 = Shock_bs2$simulation$mk_ds
nben_h_un_bs2 = Shock_bs2$simulation$nben_h_un
ur_bs2 = Shock_bs2$simulation$ur
net_balance_bs2 = xk_ds_bs2 - mk_ds_bs2
net_balance_bs2_ratio= (xk_ds_bs2 - mk_ds_bs2)/yk_ds_bs2

@@

```{r}
###Gengivelse af stød til model
max_dp_bs3 = Shock_bs3$simulation$max_dp
wage_bs3 = Shock_bs3$simulation$wage
komp_r_bs3 = Shock_bs3$simulation$komp_r
part_bs3 = Shock_bs3$simulation$part
yk_bs3 = Shock_bs3$simulation$yk
yk_ds_bs3 = Shock_bs3$simulation$yk_ds
pc_ds_bs3 = Shock_bs3$simulation$pc_ds
wage_ds_t_bs3 = Shock_bs3$simulation$wage_ds_t
ur_ds_bs3 = Shock_bs3$simulation$ur_ds
emp_bs3 = Shock_bs3$simulation$emp
yd_hk_ds_bs3 = Shock_bs3$simulation$yd_hk_ds
nben_h_un_bs3 = Shock_bs3$simulation$nben_h_un
prodk_bs3 = Shock_bs3$simulation$prodk
tilpas_pr_bs3 = Shock_bs3$simulation$tilpas_pr
u_ds_bs3 = Shock_bs3$simulation$u_ds
part_bs3 = Shock_bs3$simulation$part
nben_h_bs3 = Shock_bs3$simulation$nben_h
wage_ds_bs3 = Shock_bs3$simulation$wage_ds
dp_person_bs3 = Shock_bs3$simulation$dp_person
kont_h_ratio_bs3 = Shock_bs3$simulation$kont_h_ratio
lf_bs3 = Shock_bs3$simulation$lf
nl_g_bs3 = Shock_bs3$simulation$nl_g
unemp_bs3 = Shock_bs3$simulation$unemp
s_h_bs3 = Shock_bs3$simulation$s_h
inflation_bs3 = Shock_bs3$simulation$inflation
y_bs3 = Shock_bs3$simulation$y
yd_hk_ds_bs3 = Shock_bs3$simulation$yd_hk_ds
wage_gap1_bs3 = Shock_bs3$simulation$wage_gap1
wage_gap_bs3 = Shock_bs3$simulation$wage_gap
prod_bs3 = Shock_bs3$simulation$prod
prod_ds_bs3 = Shock_bs3$simulation$prod_ds
prod_ds_shock_bs3 = Shock_bs3$simulation$prod_ds_shock

@@

shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q')
)

@@

```{r}
###Gengivelse af stød til model
max_dp_bs4 = Shock_bs4$simulation$max_dp
wage_bs4 = Shock_bs4$simulation$wage
komp_r_bs4 = Shock_bs4$simulation$komp_r
part_bs4 = Shock_bs4$simulation$part
yk_bs4 = Shock_bs4$simulation$yk
yk_ds_bs4 = Shock_bs4$simulation$yk_ds
pc_ds_bs4 = Shock_bs4$simulation$pc_ds
wage_ds_t_bs4 = Shock_bs4$simulation$wage_ds_t
ur_ds_bs4 = Shock_bs4$simulation$ur_ds
emp_bs4 = Shock_bs4$simulation$emp
yd_hk_ds_bs4 = Shock_bs4$simulation$yd_hk_ds
lf_bs4 = Shock_bs4$simulation$lf
tilpas_pr_bs4 = Shock_bs4$simulation$tilpas_pr
u_ds_bs4 = Shock_bs4$simulation$u_ds
part_bs4 = Shock_bs4$simulation$part
nben_h_bs4 = Shock_bs4$simulation$nben_h
wage_ds_bs4 = Shock_bs4$simulation$wage_ds
dp_person_bs4 = Shock_bs4$simulation$dp_person
kont_h_ratio_bs4 = Shock_bs4$simulation$kont_h_ratio
ur_bs4 = Shock_bs4$simulation$ur
nl_g_bs4 = Shock_bs4$simulation$nl_g
unemp_bs4 = Shock_bs4$simulation$unemp
s_h_bs4 = Shock_bs4$simulation$s_h
inflation_bs4 = Shock_bs4$simulation$inflation
y_bs4 = Shock_bs4$simulation$y
yd_hk_ds_bs4 = Shock_bs4$simulation$yd_hk_ds
wage_gap1_bs4 = Shock_bs4$simulation$wage_gap1
wage_gap_bs4 = Shock_bs4$simulation$wage_gap
prod_bs4 = Shock_bs4$simulation$prod
prod_ds_bs4 = Shock_bs4$simulation$prod_ds
prod_ds_shock_bs4 = Shock_bs4$simulation$prod_ds_shock

@@

```{r}
###Gengivelse af stød til model
max_dp_01 = Shock_1$simulation$max_dp
yk_ds_01 = Shock_1$simulation$yk_ds
wage_01 = Shock_1$simulation$wage
komp_r_01 = Shock_1$simulation$komp_r
part_01 = Shock_1$simulation$part
yk_01 = Shock_1$simulation$yk
pc_ds_01 = Shock_1$simulation$pc_ds
wage_ds_t_01 = Shock_1$simulation$wage_ds_t
ur_ds_01 = Shock_1$simulation$ur_ds
emp_01 = Shock_1$simulation$emp
yd_hk_ds_01 = Shock_1$simulation$yd_hk_ds
nben_h_un_01 = Shock_1$simulation$nben_h_un
lf_01 = Shock_1$simulation$lf
tilpas_pr_01 = Shock_1$simulation$tilpas_pr
u_ds_01 = Shock_1$simulation$u_ds
part_01 = Shock_1$simulation$part
nben_h_01 = Shock_1$simulation$nben_h
wage_ds_01 = Shock_1$simulation$wage_ds
dp_person_01 = Shock_1$simulation$dp_person

ur_01 = Shock_1$simulation$ur
nl_g_01 = Shock_1$simulation$nl_g
unemp_01 = Shock_1$simulation$unemp
yd_hk_ds_01 = Shock_1$simulation$yd_hk_ds
wage_gap1_01 = Shock_1$simulation$wage_gap1
wage_gap_01 = Shock_1$simulation$wage_gap
prod_01 = Shock_1$simulation$prod
```

```{r}
plot(part_01, col= "red"); lines(part_bs1, col = "blue");
legend("top",legend=c("Baseline", "Data"),lty=c(1,1),lwd=c(2),bty="n", col = c("red", "blue")); 
grid()
```

@@

plot(((yk_ds_01 - yk_ds_bs1) / yk_ds_bs1), col= "black", xlab= "Year", ylab= "% Change in gdp");
legend("top", legend=c("GDP"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()

plot(((unemp_01 - unemp_bs1) / unemp_bs4), col= "black", xlab= "Year", ylab= "% Change in employment");
legend("top", legend=c("Employment"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()
```

@@

nben_h_un_02 = Shock_2$simulation$nben_h_un
yk_02 = Shock_2$simulation$yk
yk_ds_02 = Shock_2$simulation$yk_ds
emp_02 = Shock_2$simulation$emp
wage_ds_02 = Shock_2$simulation$wage_ds
ur_ds_02 = Shock_2$simulation$ur_ds
pc_ds_02 = Shock_2$simulation$pc_ds
yd_hk_ds_02 = Shock_2$simulation$yd_hk_ds
pconk_ds_02 = Shock_2$simulation$pconk_ds
komp_r_02 = Shock_2$simulation$komp_r
max_dp_02 = Shock_2$simulation$max_dp
nben_h_02 = Shock_2$simulation$nben_h
yd_hk_ds_02 = Shock_2$simulation$yd_hk_ds
ik_02 = Shock_2$simulation$ik
wage_ds_t_02 = Shock_2$simulation$wage_ds_t
nben_h_un_02 = Shock_2$simulation$nben_h_un
nl_g_02 = Shock_2$simulation$nl_g
nsben_h_02 = Shock_2$simulation$nsben_h
dp_person_02 = Shock_2$simulation$dp_person
xk_ds_02 = Shock_2$simulation$xk_ds
mk_ds_02 = Shock_2$simulation$mk_ds
ik_02 = Shock_2$simulation$ik
rer_02 = Shock_2$simulation$rer
ps_ds_02 = Shock_2$simulation$ps_ds
i_bd_nfc_k_ds_02 = Shock_2$simulation$i_bd_nfc_k_ds
yd1_hk_ds_02 = Shock_2$simulation$yd1_hk_ds
yd2a_hk_ds_02 = Shock_2$simulation$yd2a_hk_ds
yd2b_hk_02 = Shock_2$simulation$yd2b_hk
i_equip_nfc_k_ds_02 = Shock_2$simulation$i_equip_nfc_k_ds
u_ds_02 = Shock_2$simulation$u_ds
wage_gap1_02 = Shock_2$simulation$wage_gap1
gk_02 = Shock_2$simulation$gk
kont_h_ratio_02 = Shock_2$simulation$kont_h_ratio
lf_02 = Shock_2$simulation$lf
ur_02 = Shock_2$simulation$ur
wage_gap_02 = Shock_2$simulation$wage_gap
max_gap_02 = Shock_2$simulation$max_gap
unemp_02 = Shock_2$simulation$unemp
inflation_02 = Shock_2$simulation$inflation
prod_02 = Shock_2$simulation$prod
ws_02 = Shock_2$simulation$ws
net_balance_02 = xk_ds_02 - mk_ds_02
```

```{r, fig.width=10, fig.height=8}
par(mfrow=c(2,2))
plot((wage_ds_01-wage_ds_bs1), col= "red");lines((wage_ds_02-wage_ds_bs2), col= "blue")

plot((yk_01-yk_bs1), col= "red");lines((yk_02-yk_bs2), col= "blue")

plot((emp_01-emp_bs1)*1000, col= "red", ylim= c(-1000,1000)); lines((emp_02-emp_bs2)*1000, col= "blue")

plot((pc_ds_01-pc_ds_bs1), col= "red"); lines((pc_ds_02-pc_ds_bs2), col= "blue")
```

```{r, fig.width=10, fig.height=8}
par(mfrow=c(2,2))
plot((unemp_01-unemp_bs1)*1000, col= "red");lines((unemp_02-unemp_bs2)*1000, col= "blue")

plot((lf_01-lf_bs1)*1000, col= "red");lines((lf_02-lf_bs2)*1000, col= "blue")

plot((emp_01-emp_bs1)*1000, col= "red"); lines((emp_02-emp_bs2)*1000, col= "blue")

plot((ur_01-ur_bs1), col= "red"); lines((ur_02-ur_bs2), col= "blue")
```

```{r, fig.width=10, fig.height=8}
par(mfrow=c(2,2))
plot((wage_ds_01-wage_ds_bs1)*1000, col= "red");lines((wage_ds_02-wage_ds_bs2)*1000, col= "blue")

plot((lf_01-lf_bs1)*1000, col= "red");lines((lf_02-lf_bs2)*1000, col= "blue")

plot((emp_01-emp_bs1)*1000, col= "red"); lines((emp_02-emp_bs2)*1000, col= "blue")

plot((ur_01-ur_bs1), col= "red"); lines((ur_02-ur_bs2), col= "blue")
```

@@

```{r}
###Gengivelse af stød til model
y_03 = Shock_3$simulation$y
yk_03 = Shock_3$simulation$yk
yk_ds_03 = Shock_3$simulation$yk_ds
emp_03 = Shock_3$simulation$emp
wage_ds_03 = Shock_3$simulation$wage_ds
ur_ds_03 = Shock_3$simulation$ur_ds
pc_ds_03 = Shock_3$simulation$pc_ds
yd_hk_ds_03 = Shock_3$simulation$yd_hk_ds
pconk_ds_03 = Shock_3$simulation$pconk_ds
komp_r_03 = Shock_3$simulation$komp_r
max_dp_03 = Shock_3$simulation$max_dp
nben_h_03 = Shock_3$simulation$nben_h
yd_hk_ds_03 = Shock_3$simulation$yd_hk_ds
ik_03 = Shock_3$simulation$ik
wage_ds_t_03 = Shock_3$simulation$wage_ds_t
nben_h_un_03 = Shock_3$simulation$nben_h_un
nl_g_03 = Shock_3$simulation$nl_g
nsben_h_03 = Shock_3$simulation$nsben_h
dp_person_03 = Shock_3$simulation$dp_person
part1_03 = Shock_3$simulation$part1
u_ds_03 = Shock_3$simulation$u_ds
kont_h_ratio_03 = Shock_3$simulation$kont_h_ratio
part_03 = Shock_3$simulation$part
unemp_03 = Shock_3$simulation$unemp
rw_ds_03 = Shock_3$simulation$rw_ds
kuld_03 = Shock_3$simulation$shock_kuld
inflation_03 = Shock_3$simulation$inflation
lf_03 = Shock_3$simulation$lf
prod_03 = Shock_3$simulation$prod
nben_h_un_03 = Shock_3$simulation$nben_h_un
ur_03 = Shock_3$simulation$ur
prodk_03 = Shock_3$simulation$prodk
```

@@

```{r}
# Define add-factor list (defining shock)
constantAdjList_4 <- list(
 shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q')
)

@@

```{r, fig.width=10, fig.height=10}
par(mfrow=c(2,2))
plot((unemp_01-unemp_bs1)*1000, col= "red",  ylim= c(-500,500));lines((unemp_04-unemp_bs4)*1000, col= "blue")

plot((lf_01-lf_bs1)*1000, col= "red", ylim= c(-500,500));lines((lf_04-lf_bs4)*1000, col= "blue")

plot((emp_01-emp_bs1)*1000, col= "red", ylim= c(-1000,1000)); lines((emp_04-emp_bs4)*1000, col= "blue")

plot((ur_01-ur_bs1), col= "red", ylim= c(-0.0001,0.0002)); lines((ur_04-ur_bs4), col= "blue")
```

```{r, fig.width=10, fig.height=8}
par(mfrow=c(2,2))
plot((unemp_03-unemp_bs3)*1000, col= "red",  ylim= c(-500,500));lines((unemp_04-unemp_bs4)*1000, col= "blue")

plot((lf_03-lf_bs3)*1000, col= "red", ylim= c(-500,500));lines((lf_04-lf_bs4)*1000, col= "blue")

plot((emp_03-emp_bs3)*1000, col= "red", ylim= c(-1000,1000)); lines((emp_04-emp_bs4)*1000, col= "blue")

plot((ur_03-ur_bs3), col= "red", ylim= c(-0.0001,0.0002)); lines((ur_04-ur_bs4), col= "blue")
```

```{r, fig.width=10, fig.height=8}
par(mfrow=c(2,2))
plot((y_03-y_bs3), col= "red");lines((y_04-y_bs4), col= "blue")

plot((yk_03-yk_bs3), col= "red");lines((yk_04-yk_bs4), col= "blue")
